The population of long-period exoplanets --- \\ Fully-automated discovery \& characterization of long-period transiting exoplanet candidates in the \kepler\ archive \vspace{-3\baselineskip}

### 2016-06-30 document/ms.tex

>>>>

\paragraph{Priors}

For each candidate in our sample, we take the constraints on the stellar
parameters from the \kepler\ stellar properties catalog\footnote{The
\textsf{q1\_q17\_dr24\_stellar} table from the NASA Exoplanet Archive
\citep{Huber:2014}} and assume an empirical beta function prior on the
eccentricities based on the observed eccentricity distribution of long-period
planets discovered using radial velocities \citep{Kipping:2013}.
Table~\ref{tab:parameters} lists all the fit parameters and their prior
distributions.
Besides these listed priors, we add the extra constraint that no other
transits can occur in the baseline of the \kepler\ observations.
This constraint is overly conservative because there is some probability that
a second transit could occur in a data gap but we find that, in practice, most
of the posterior mass is at longer periods and the period inferences are not
significantly affected.

\paragraph{Likelihood function}
